Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Plot England all_cause mortality rates

#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)

@@

#Greater London (GL)
GBDGL <- filter(GBDdata, location == "greater london" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)
GBDGL$one_rate <- GBDGL$val/100000
```

>>>>

#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, cause, val, age_cat)

@@

#Greater London (GL)
GBDGL <- filter(GBDdata, location == "greater london" & metric == "rate") %>% select(measure, location, sex, age, metric, cause, val, age_cat)
GBDGL$one_rate <- GBDGL$val/100000
```

These graphs are to compare GBD data for England and Greater London.

```{r, echo=FALSE}

mx_plot_compare <- ggplot(data = filter(GBDEngland, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat), aes(x = age_cat)) +
    geom_line(mapping = aes(y = one_rate, colour = "one_rate")) +
  theme_classic()

#Print to view
print(mx_plot_compare)

```
